Three 38 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-02-28 papers/ms.tex
stage Cep-Her outline

%\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
%\documentclass[12pt,modern,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

\newcommand{\cn}{$\delta$\ Lyr\ cluster} % cluster name
\newcommand{\sn}{Kepler\,1627} % star system name (binary)
\newcommand{\pn}{Kepler\,1627Ab} % planet name

@@

% gaia target sample numbers
\newcommand{\nkinematic}{1{,}201} % deltalyr_kc19_cleansubset_withreddening.csv
% all from oneoff_calculate_rotation_numbers.py
\newcommand{\noriginal}{3{,}071} % Vizier; KC19 Theia 73 member count
\newcommand{\nwithtess}{924} % How many stars have TESS data with G<17 and (Bp-Rp)0 > 0.5?
\newcommand{\nforgyro}{1842} % How many stars have G<17 and (Bp-Rp)0 > 0.5?
\newcommand{\nkinwithtess}{391} % How many kinematically selected stars have TESS data?
\newcommand{\nkinwithtessandcrowding}{192} % How many kinematically selected stars have TESS data and meeting the crowding cutoff (nequal<=0, nclose<=1)?
\newcommand{\nkindefaultcleaning}{145} % How many of these meet the "defaultcleaning" criteria (LSP>0.1, Prot<15, and crowding cut)?
\newcommand{\nrotgood}{135} % nkindefaultcleaning, minus outliers.
\newcommand{\nfracprot}{70} % fraction nrotgood/nkinwithtessandcrowding

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{2021 Oct 12}
\revised{2021 Dec 6}
\accepted{2021 Dec 27}
%\submitjournal{AAS Journals}
\shorttitle{Kepler\,1627}

@@

\title{
  A 38 Million Year Old Neptune-Sized Planet in the Kepler Field
}

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.8\,R_\oplus$ \replaced{mini-Neptune}{planet} on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show using
  Gaia kinematics, TESS stellar rotation periods, and spectroscopic
  lithium abundances that Kepler\,1627 is a member of the \clusterage\
  old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found by
  the \replaced{main}{prime} Kepler mission.  The Kepler photometry shows two
  peculiarities: the average transit profile is asymmetric, and the
  individual transit times might be correlated with the local light curve
  slope.  We discuss possible explanations for each anomaly.  More
  importantly, the $\delta$~Lyr cluster
  is one of $\sim$10$^3$ coeval groups whose properties have been clarified
  by Gaia.  Many other exoplanet hosts are candidate members
  of these clusters; their ages can be verified \replaced{through}{with} the
  trifecta of Gaia, TESS, and ground-based spectroscopy.
\end{abstract}

@@

@@

While thousands of exoplanets have been discovered orbiting nearby
stars, the vast majority of them are several billion years old.  This
makes it difficult to test origin theories for the different families
of planets, since many evolutionary processes are expected to operate
on timescales of less than 100 million years.

For instance, the ``mini-Neptunes'', thought to be made of metal
cores, silicate mantles \citep{kite_atmosphere_2020}, and extended
hydrogen-dominated atmospheres, are expected to shrink
in size by factors of several over their first $10^8$ years.
Specifically, in the models of \citet{owen_atmospheres_2016} and
\citet{owen_constraining_2020}, the $\approx$$5\,M_\oplus$ planets start
with sizes of 4\,--\,12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2\,--\,4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years after the disk
disperses \citep{ikoma_situ_2012}, stellar
irradiation and internal heat can also power gradual outflows
which, if strong enough, can deplete or entirely strip the atmosphere \citep{lopez_how_2012,Owen_Wu_2013,ginzburg_corepowered_2018}.\added{ The photoevaporative and core-powered
	outflows are thought to persist for $\approx$$10^8$ to $\approx$$10^9$ years,
	though the details depend on the planetary masses,
	the irradiation environments, and the initial atmospheric
	mass fractions \citep{owen_evaporation_2017,gupta_signatures_2020,2021MNRAS.503.1526R,2021MNRAS.501L..28K}.} Discovering young planets, measuring their masses, and detecting their
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017,van_eylen_asteroseismic_2018}.

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020,martioli_aumicbc_2021}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
during the \replaced{main}{prime} Kepler mission (2009--2013), only four open clusters
were known in the Kepler field,
%: NGC\,6866, NGC\,6811, NGC\,6819, and NGC\,6791,
with ages spanning 0.7\,Gyr to 9\,Gyr \citep{meibom_kepler_2011}.
Though isochronal, gyrochronal, and lithium-based analyses suggest
that younger Kepler planets do exist
\citep{walkowicz_rotation_2013,berger_identifying_2018,david_sizes_2021}, accurate and precise
age measurements typically require an ensemble of stars.  Fortunately,
recent analyses of the Gaia data have greatly expanded our knowledge
of cluster memberships \citep[{\it
e.g.},][]{CantatGaudin2018a,Zari2018,KounkelCovey2019,Meingast2021,Kerr2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

Matching our young star list against stars observed by Kepler revealed
that Kepler observed a portion of the \cn\ (Stephenson-1; Theia~73).
More specifically, a clustering analysis of the Gaia data by
\citet{KounkelCovey2019} reported that Kepler~1627 (KIC 6184894; KOI
5245) is a \cn\ member.  Given the previous statistical
validation of the close-in \replaced{mini-Neptune}{Neptune-sized
planet} Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by scrutinizing the properties of the cluster
(Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr cluster is
\clusterage\ old, and in Section~\ref{sec:stars} show that \sn\ is
both a binary and also a member of the cluster.  Focusing on the
planet (Section~\ref{sec:planet}), we confirm that despite the
existence of the previously unreported \replaced{M2.5}{M3}V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.
We also analyze an asymmetry in the average transit profile, and a
possible correlation between the individual transit times and the
local light curve slope.  We conclude by discussing broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities of stars in the
    $\delta$\,Lyr cluster.} Points are reported cluster members from
    \citet{KounkelCovey2019}.  The tangential velocities relative to
    \sn\ (bottom right) are computed assuming that every star has the
    same three-dimensional spatial velocity as \sn.  Our analysis
    considers stars (black points) in the spatial and kinematic
    vicinity of Kepler\,1627 (yellow star).  The question of whether
    the other candidate cluster members (gray points) are part of the
    cluster is outside our scope.  The location of the Sun is
    ($\odot$) is shown \added{to clarify the direction along which
    parallax uncertainties are expected to produce erroneous
    clusters}.
		\label{fig:XYZvtang}
	}
\end{figure*}

To measure the age of the $\delta$ Lyr cluster, we first selected a
set of candidate cluster members
(Section~\ref{sec:kinematicselection}), and then analyzed these stars
using a combination of the isochronal and gyrochronal techniques
(Section~\ref{sec:clusterage}).

@@

\citet{KounkelCovey2019} applied an unsupervised clustering algorithm
to Gaia DR2 on-sky positions, proper motions, and parallaxes for stars
within the nearest kiloparsec.  For the \cn\ (Theia 73), they reported
\noriginal\ candidate members.  We matched these stars against the
latest Gaia EDR3 observations using the \texttt{dr2\_neighbourhood}
table from the ESA archive,
taking the stars closest in proper motion and epoch-corrected angular
distance as the presumed match \citep{gaia_collaboration_2021_edr3}.
\replaced{In Figure~\ref{fig:XYZvtang}, \added{we }have shown galactic positions only for
the stars with parallax signal-to-noise exceeding 20. }{For plotting purposes, we focused only
on the stars with parallax signal-to-noise exceeding 20.} \added{We
calculated the tangential velocities for each of these stars relative to \sn\
($\Delta \mu^{*}$) by subtracting the observed proper motion from what the proper motion at each star's
position would be if it were co-moving with \sn. }

\replaced{The}{Figure~\ref{fig:XYZvtang} shows that the} reported
cluster members (gray and black points) extend over a much larger
volume \added{in both physical and kinematic space }than the cluster previously identified by
\citet{stephenson_possible_1959} and later corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps'' of
stars might comprise a {\it bona fide} cluster of identically-aged
stars, they could also be heavily contaminated by field stars.
\added{One reason to suspect this is that the spread in tangential
velocities exceeds typical limits for kinematic coherence
\citep{Meingast2021}}.
We
therefore considered stars only in the immediate kinematic and spatial
vicinity of \sn\ as candidate cluster members.  We performed
\replaced{the}{this}
selection cut\deleted{s} manually, by drawing lassos with the interactive
\texttt{glue} visualization tool \citep{beaumont_2014_13866} in the
four projections shown in Figure~\ref{fig:XYZvtang}.  The overlap
between the Kepler field and the resulting candidate cluster members
is shown in Figure~\ref{fig:skychart}.  While this method will include
some field interlopers in the ``cluster star'' sample, and vice-versa,
it should suffice for our aim of verifying the existence of the
cluster in the vicinity of \sn.
%\added{The application of a more careful membership selection procedure to the $\delta$\ Lyr\ cluster (as part of a larger complex spanning Cepheus and Hercules) is a topic under current investigation by by R.~Kerr and collaborators.}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler's view of the $\delta$~Lyr cluster, shown in equatorial
    	coordinates.} Each black circle
    is a candidate cluster member selected based on its position and kinematics (Figure~\ref{fig:XYZvtang}).  Of
    the \nkinematic\ candidate cluster members, 58 have at least one
    quarter of Kepler data.  TESS has also observed most of the
    cluster, for one to two lunar months to date.
		\label{fig:skychart}
	}
\end{figure}

@@

We measured the isochrone age using an empirical approach.  The \added{upper }left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD) of candidate \cn\ members, IC\,2602\added{ ($\approx 38$\,Myr)}, the Pleiades\added{ ($\approx 115$\,Myr)}, and
the field. The stars from the Pleiades and IC\,2602 were adopted from
\citet{CantatGaudin2018a}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.\added{ We also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).
We adopted the UCL members from \citet{Damiani2019}.
For visual clarity, the latter two clusters are not shown in Figure~\ref{fig:age}.} We cleaned \replaced{these}{the membership lists}
following the data filtering criteria from \citet[][Appendix
B]{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  \added{This also involved cuts
on the photometric signal to noise ratio, the number of visibility
periods used, the astrometric $\chi^2$ of the single-source solution, and the
$G_{\rm BP}-G_{\rm RP}$ color excess factor.} These filters were
designed to include genuine binaries while omitting instrumental
artifacts.

\replaced{We then corrected for extinction by querying}{To correct for extinction, we queried} the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/},
2021/09/25}, and applied the extinction coefficients $k_X\equiv
A_X/A_0$ computed by \citet{GaiaCollaboration2018} assuming that $A_0
= 3.1 E(B-V)$.  For \added{UCL, }IC\,2602, the Pleiades, and the \cn, this
procedure yielded a respective mean and standard deviation for the
reddening of \replaced{$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008,
0.032\pm0.006\}$}{$E(B-V)=\{0.084\pm0.041, 0.020\pm0.003, 0.045\pm0.008,
0.032\pm0.006\}$}.
These values \replaced{agree reasonably well with}{are within a
factor of two of} previously reported values
\replaced{from}{in} the literature \citep{pecaut_star_2016,GaiaCollaboration2018,KounkelCovey2019,bossini_age_2019}\added{, and are all small enough that the choice of whether to use them {\it vs.} other
extinction estimates does not affect our primary conclusions}.

% Gaia+2018 E(B-V):
% Pleiades 0.045, IC2602 0.031
%
% Randich+2018 E(B-V):
% Pleiades ??, IC2602 0.032 - 0.092
%
% KC2019: AV->E(B-V)
% Pleiades 0.220 AV -> 0.071
% IC2602 0.243297 -> 0.078
% Stephenson1 0.184 -> 0.059
%
% Bossini+2019 AV->E(B-V)
% PleiadesMelotte22 0.140 -> 0.045
% IC2602 0.096 -> 0.031
% Steph1: 0.157 -> 0.051

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f3a.pdf}
			\includegraphics[width=0.469\textwidth]{f3b.pdf}
		}

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f3c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The \cn\ is \clusterage\ old.}  {\it Top:} Color-absolute
		magnitude diagram of candidate \cn\ members, in addition to stars
		in IC\,2602 ($\approx38$\,Myr), the Pleiades ($\approx 115$\,Myr),
		and the Gaia EDR3 Catalog of Nearby Stars (gray background).  The
		zoomed right panel highlights the pre-main-sequence.  The \cn\ and
		IC\,2602 are approximately the same isochronal age.  {\it Bottom:}
		TESS and Kepler stellar rotation period versus dereddened Gaia
		color, with the Pleiades and Praesepe (650\,Myr) shown for
		reference \citep{rebull_rotation_2016a,douglas_poking_2017}.  Most
		candidate \cn\ members are gyrochronally younger than the
		Pleiades; outliers are probably field interlopers.
		\label{fig:age}
	}
\end{figure*}

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and
therefore are approximately the same age.  \replaced{In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}). The
pre-main-sequence M dwarfs of the \cn\ were intermediate between the
latter two clusters.}{The
pre-main-sequence M dwarfs of a fixed color in the \cn\ are more luminous than those of the Pleiades, and were also seen to be 
less luminous than those in
UCL.}  To turn this heuristic interpolation
into \replaced{an age}{a quantitative age}
measurement, we used the empirical method developed by
\citet{gagne_mutau_2020}.  In brief, we fitted the pre-main-sequence
loci of a set of reference clusters, and the locus of the target \cn\
was then modeled as a piecewise linear combination of these reference
clusters.  For our reference clusters, \replaced{we adopted members of UCL,
IC\,2602, and the Pleiades from \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively}{we used UCL, IC\,2602, and the
Pleiades}.  We removed binaries by
requiring $\texttt{RUWE}<1.3$, $\texttt{radial\_velocity\_error}$
below the 80$^{\rm th}$ percentile of each cluster's distribution, and
excluded stars that were obvious photometric binaries in the CAMD.\footnote{
  For a description of the renormalized unit weight error (RUWE), see the GAIA DPAC technical note
  \url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}.}  We then passed a
moving box average and standard deviation across the CAMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid
of \deleted{hybrid }isochrones spanning the ages between UCL \replaced{to}{and} the Pleiades using
Equation\replaced{s~6 and~7}{~6} from
\citet{gagne_mutau_2020}.  
\added{To derive a probability distribution function for the age of \cn, we
then assumed a Gaussian likelihood that treated the interpolated isochrones as
the ``model'' and the $\delta$\ Lyr\ cluster's isochrone as the ``data''
(Equation~7 from \citealt{gagne_mutau_2020}).  The cluster's age and its
statistical uncertainty are then quoted as the the mean and standard deviation
of this age posterior.}

% Randich+18: 43.7 +4.3 - 3.9 LDB
% Dobbie+10: 46 +6 -5 LDB

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades
\citep{dahm_2015}, and a 16\,Myr age for UCL \citep{pecaut_star_2016}.
The age of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with older ages being preferred by
the lithium-depletion-boundary (LDB) measurements
\citep{dobbie_ic_2010,randich_gaiaeso_2018} and younger ages by the
main-sequence turn-off
\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.  If
we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would be
$31^{+5}_{-4}$\,Myr old.  For the converse extreme of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age for IC\,2602, which yields an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST isochrone
models over a grid of ages, metallicities, and reddenings, yielded the
best agreement for this $\approx$$38\,$Myr age as well, given ${\rm
[Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CAMD
reddening is higher than the \citet{lallement_threedimensional_2018}
value by a factor of two.  } Follow-up studies of the LDB or
main-sequence turn-off in the \cn\ could help determine a more precise
and accurate age for the cluster, and are left for future work.

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{KounkelCovey2019}, \nwithtess\ stars were amenable to rotation
period measurements ($G<17$ and $\bpmrpo>0.5$) using the TESS full
frame image data.\added{ As a matter of
scope, we restricted our attention to the \nkinwithtess\ stars
discussed in Section~\ref{sec:kinematicselection} in the spatial and
kinematic proximity of Kepler\,1627.} We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (a radius of 1 TESS pixel).
Within this radius, we recorded the number of stars with greater
brightness than the target star, and with brightness within 1.25 TESS magnitudes of the target star.

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.\deleted{ As a
matter of scope, we restricted our attention to the \nkinwithtess\
stars discussed in Section~\ref{sec:kinematicselection} in the spatial
and kinematic proximity of Kepler\,1627.}\deleted{ Kepler rotation
periods were derived by \citet{mcquillan_rotation_2014} for 28 of
our \nkinwithtess\ stars; for these cases, we
simply adopted the Kepler rotation period.}\added{ First, to validate
the TESS rotation periods, we compared against 28 stars
from \citet{mcquillan_rotation_2014} that were also observed by Kepler.  Of the 23 stars with Kepler
periods below 10 days, 21 of the TESS periods agreed with the Kepler
rotation periods; the other 2 were measured at the double-period
harmonic.  Of the remaining 5 stars with Kepler rotation periods above
10 days, none were correctly recovered by TESS, and 3 were near the
half-period harmonic.  We were therefore 
wary of any TESS rotation periods exceeding 10 days, and used the
Kepler rotation periods whenever possible.}
For the remaining stars with only TESS data, we
focused only on the stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these crowding requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  
The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a gyrochronal
age for the \cn\ below 100\,Myr.  In fact, the rotation-color
distributions of other 30\,Myr to 50\,Myr clusters ({\it e.g.},
IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}.  Approximately 10 of the
\cn\ stars appear as outliers above the ``slow sequence''.  Assuming
that they are all false positives ({\it i.e.}, field interlopers), our
rotation period detection fraction would be
$\nrotgood/\nkinwithtessandcrowding \approx \nfracprot\%$.   \replaced{The other
stars are likely to be field contaminants.}{Although some of these outlier stars might be
unresolved F+K binaries that are in the cluster
\citep{stauffer_rotation_2016}, assuming that they are field contaminants
provides a more secure lower bound of the rotation period detection fraction.}  A final possible
confounding factor -- binarity -- is known to affect the ``fast
sequence'' of stars beneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.  We do
not expect it to change the central conclusion regarding the cluster's
age.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f4a.pdf}
			\includegraphics[width=0.48\textwidth]{f4b.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Kepler 1627 is a binary.} {\it Left:} High-resolution imaging
		from Gemini-North/`Alopeke and Keck/NIRC2 shows an $\approx$\replaced{M2.5}{M3}V
		companion at $\rho \approx 0\farcs16$, which corresponds to a
		projected separation of $53\pm4$\,AU.  The inset shows a cutout of
		the stacked NIRC2 image (North is up, East is left, scale is set
		by the separation of the binary).  The lines show 5-$\sigma$
		contrast limits for the `Alopeke filters, and 6-$\sigma$ contrast
		limits for NIRC2 outside of $0\farcs15$. {\it Right:} Gaia EDR3
		renormalized unit weight error (RUWE) point estimates for
		candidate $\delta$\,Lyr cluster members.  Since other members of
		the cluster with similar brightnesses have comparable degrees of
		photometric variability, the high RUWE independently suggests that
		Kepler\,1627 is a binary. 
		\label{fig:kep1627binary}
	}
\end{figure*}

\subsection{Kepler\,1627A}
\subsubsection{Age}
% rotation period from plot_rotation_period_windowslider.py
Based on the spatial and kinematic association of \sn\ with the \cn,
and the assumption that the planet formed shortly after the star, it
seems likely that \sn\ is the same age as the cluster. There are two
consistency checks on whether this is true: rotation and lithium.
Based on the Kepler light curve, the rotation period is
$2.642\pm0.042$\,days, where the quoted uncertainty is based on the
scatter in rotation periods measured from each individual Kepler
quarter.  This is consistent with comparable cluster members
(Figure~\ref{fig:age}).

To infer the amount of Li\,\textsc{I} from the 6708\,\AA\ doublet
\citep[{\it e.g.},][]{soderblom_ages_2014}, we acquired an iodine-free
spectrum from Keck/HIRES on the night of 2021 March 26 using the
standard setup and reduction techniques of the California Planet
Survey \citep{howard_cps_2010}.  Following the equivalent width
measurement procedure described by \citet{bouma_2021_ngc2516}, we find
${\rm EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   This value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Nonetheless,
given the stellar effective temperature (Table~\ref{tab:starparams}),
this measurement is in agreement with expectations for a
$\approx40$\,Myr star ({\it e.g.}, as measured in IC~2602 by
\citealt{randich_gaiaeso_2018}).  It is also larger than any lithium
equivalent widths measured by \citet{berger_identifying_2018} in their
analysis of 1{,}301 Kepler-star spectra.

\subsubsection{Stellar Properties}

The adopted stellar parameters are listed in
Table~\ref{tab:starparams}.  The stellar mass, radius, and effective
temperature are found by interpolating against a 38$\,$Myr MIST
isochrone \citep{choi_mesa_2016}.  The statistical uncertainties are
propagated from the absolute magnitude (mostly originating from the
parallax uncertainty) and the color; the systematic uncertainties are
taken to be the difference between the PARSEC
\citep{bressan_parsec_2012} and MIST isochrones.  Reported
uncertainties are a quadrature sum of the statistical and systematic
components.  As a consistency check, we analyzed the aforementioned
Keck/HIRES spectrum from the night of 2021 March 26 using a
combination of \texttt{SpecMatch-Emp} for stellar properties, and
\texttt{SpecMatch-Synth} for $v\sin i$ \citep{yee_SM_2017}.  This
procedure yielded $T_{\rm eff}=5498\pm100\,{\rm K}$, $\log
g=4.6\pm0.1$, $[{\rm Fe/H}]=0.15\pm0.10$ from \texttt{SpecMatch-Emp},
and $v\sin i = 18.9\pm1.0$ from \texttt{SpecMatch-Synth}.  These
values are within the $1$-$\sigma$ uncertainties of our adopted values
from the isochrone interpolation.

\subsection{Kepler\,1627B}

We first noted the presence of a close neighbor in the \sn\ system on
2015 July 22 when we acquired adaptive optics imaging using the NIRC2
imager on Keck-II.  We used the narrow camera (FOV = 10.2\arcsec) to
obtain 8 images in the $K'$ filter ($\lambda = 2.12\,\mu$m) with a
total exposure time of 160\,s. We analyzed these data following
\citet{kraus_impact_2016}, which entailed using PSF-fitting to measure
the separation, position angle, and contrast of the candidate
companion.  The best-fitting empirical PSF template was identified
from among the near-contemporaneous observations of single stars in
the same filter.  The mean values inferred from the 8 images are
reported in Table~\ref{tab:starparams}.  To estimate the detection
limits, we analyzed the residuals after subtracting the empirical PSF
template. Within each residual image, the flux was measured through
40\,mas apertures centered on every pixel, and then the noise as a
function of radius was estimated from the RMS within concentric rings.
Finally, the detection limits were estimated from the strehl-weighted
sum of the detection significances in the image stack, and we adopted
the $6$-$\sigma$ threshold as the detection limit for ruling out
additional companions.

>>>>

%\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
\documentclass[12pt,modern,tighten]{aastex63}
%\documentclass[12pt,modern,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

\newcommand{\cn}{Cep-Her complex} % cluster name
\newcommand{\sysone}{Kepler-1627} % star system name (binary)
\newcommand{\stone}{Kepler-1627 A} % star system name (binary)
\newcommand{\plone}{Kepler-1627 Ab} % planet name
\newcommand{\systwo}{Kepler-1643} % star system name (binary)
\newcommand{\sttwo}{Kepler-1643} % star system name (binary)
\newcommand{\pltwo}{Kepler-1643 b} % planet name
\newcommand{\systhree}{KOI-7368} % star system name (binary)
\newcommand{\stthree}{KOI-7368} % star system name (binary)
\newcommand{\plthree}{KOI-7368 b} % planet name
\newcommand{\sysfour}{KOI-7913 } % star system name (binary)
\newcommand{\stfour}{KOI-7913 A} % star system name (binary)
\newcommand{\plfour}{KOI-7913 Ab} % planet name

@@

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{2021 Oct 12}
\revised{---}
\accepted{---}
%\submitjournal{AAS Journals}
\shorttitle{Kepler Mini-Neptunes in Cep-Her}

@@

\title{
  Three 38 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia
}

@@

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia
  are yielding a refined view of stellar clusters during the
  first hundred million years of their lives.
  Here we present an analysis of a group of $38 \pm 6$ million year old stars
  in the Cepheus-Hercules region, hereafter the Cep-Her complex.
  This group of stars includes four previously known Kepler Objects of
  Interest:
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$),
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), and
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$).
	Kepler-1627 is a previously validated young planet
	in a component of the Cep-Her complex called the $\delta$\ Lyr\ cluster \citep{bouma_kep1627_2022}.
	Here we focus on the latter three systems, which are in other sub-components
	of the complex (RSG5 and CH-2).
	Based on kinematic evidence from Gaia, stellar rotation periods from TESS, and spectroscopy,
	these three systems are also $38 \pm 6$ million years old.
	Based on the transit shapes and high resolution imaging, we
	statistically validate that they are all most likely planets (false positive probabilities of $6\times10^{-9}$,
	$5\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368, and
	KOI-7913 respectively).
	Supplemented by Gaia and TESS, the main Kepler mission is now contributing to the
	census of young close-in planets, and Kepler-1643 and KOI-7913 are the first
	empirical demonstration that mini-Neptunes with sizes of $\approx$2 Earth radii
	exist at ages of roughly 40 million years.
\end{abstract}

@@

% * Main text <3500 words (not including acknowledgements, appendices, or other
%   supplementary)

@@

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities of stars in the
    $\delta$\,Lyr cluster.} 
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2a.pdf}
			\includegraphics[width=0.469\textwidth]{f2b.pdf}
		}

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f2c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The \cn\ is \clusterage\ old.} 
		\label{fig:age}
	}
\end{figure*}

@@

@@

@@

\subsection{Kepler\,1627A}
\subsection{Kepler\,1643}
\subsection{KOI-7368}
\subsection{KOI-7913}
Is a binary.

\section{The Planets}
\label{sec:planet}

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3a.png}
			\includegraphics[width=0.5\textwidth]{f3b.png}
		}

		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3c.png}
			\includegraphics[width=0.5\textwidth]{f3d.png}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf planets.} 
		\label{fig:planets}
	}
\end{figure*}
